HPC--101\\Onboarding

### 2016-02-22 hpc_101/paper.tex
added queue to initial free listing
Added a slide about additional servcies, and listed MATLAB

\newcommand{\regtrademark}{\fontsize{5}{6}\selectfont \textsuperscript{\textregistered}}
\newcommand{\numlessfootnotetxt}[1]{ \let\thefootnote\relax\footnotetext{#1}}

@@

\section{Sustainability}
\subsection{Community Resources}
\begin{frame}
	\frametitle{Community Resources}
	\begin{itemize}
		\item The initial investment in the cluster provides resources for all faculty, staff, and students affiliated with the University of {\hawaii}
		\item All users can run on the publicly accessible partitions:\\ \emph{community.q, lm.q, sb.q, kill.q, htc.q}
		\item For some users, the publicly available resources may not be enough~\ldots
	\end{itemize}
\end{frame}

@@

>>>>

\newcommand{\trademark}{\fontsize{5}{6}\selectfont \textsuperscript{\texttrademark}}
\newcommand{\regtrademark}{\fontsize{5}{6}\selectfont \textsuperscript{\textregistered}}
\newcommand{\numlessfootnotetxt}[1]{ \let\thefootnote\relax\footnotetext{#1}}

@@

\section{Sustainability}
\subsection{Community Resources}
\begin{frame}
	\frametitle{Community Resources}
	\begin{itemize}
		\item The initial investment in the cluster provides resources for all faculty, staff, and students affiliated with the University of {\hawaii}
		\item All users can run on the publicly accessible partitions:\\ \emph{community.q, exclusive.q, lm.q, sb.q, kill.q, htc.q}
		\item For some users, the publicly available resources may not be enough~\ldots
	\end{itemize}
\end{frame}

@@

\section{Related Services}
\begin{frame}
\frametitle{Services}
\begin{itemize}
\item MATLAB Distributed Computing Server{\trademark}
  \begin{itemize}
    \item Requires user to already have a license for MATLAB
    \item User must also have access to at least the Parallel Computing Toolbox{\trademark}
    \item Provides users access to up to 64 workers
    \item Requires some additional configuration
    \item Email us to request access to this additional service
  \end{itemize}
\end{itemize}
\end{frame}
